Resources for Data-Driven \\Search-Based Software Engineering

### 2018-01-20 doc/tex/msr18/main.tex
Updates from ShareLaTeX

>>>>

This repository has taken several years to build. Prior to this collection, we were forced to test out our data-driven SBSE
prototypes on tiny toy tasks such as the ZDT and DTLZ suite. These toy tasks have some useful
properties (e.g. the DTLZ tasks can expand to any number of decisions and objectives),
they proved not to be of interest to reviewers from SE venues.
